References

### 2015-03-20 cv/XieXiaolei-Analyst.tex
Add the revised CV.

\section*{My Goal}
A self-funded Ph.D student of Finance \& Insurance mathematics
at KU, who is very experienced in programming and statistical analysis, is
looking for a part-time job as a quantitative analyst.

\section*{Education}
\begin{itemize}
\item Ph.D of Finance \& Insurance Mathematics, October 2014 - present
  \begin{itemize}
    \item {\it Reseach Areas:} I am mainly interested in the
      determination of the largest eigenvalues of a covariance matrix
      of samples with heavy-tails. The purpose is dimension
      reduction, by which the behaviour of a diverse portfolio is
      replicated by one with much few components and hence analysis of
      the portfolio becomes more simplified and focused.

>>>>

\section*{My Goal}
A Ph.D student of Economic \& Insurance mathematics at Copenhagen
University, who is very experienced in programming and statistical
analysis, is looking for a part-time job as a quantitative analyst.

\section*{Education}
\begin{itemize}
\item Ph.D of Finance \& Insurance Mathematics, October 2014 - present
  \begin{itemize}
    \item {\it Reseach Areas:} I am mainly interested in the
      determination of the largest eigenvalues of a covariance matrix
      of samples with heavy-tails. The purpose is dimension
      reduction, by which the behaviour of a diverse portfolio is
      replicated by one with much fewer components and hence analysis
      of the portfolio becomes more simplified and focused.
